When does vapor pressure deficit drive or reduce evapotranspiration?

### 2019-09-05 doc/paper/james-response-to-reviewers.tex

\documentclass[12pt]{article}

\input{preamble}

\begin{document}

\large \textbf{Response to Reviewers: \textit{When does vapor pressure deficit drive or reduce
    evapotranspiration?}} \\
Adam Massmann, Pierre Gentine, and Changjie Lin \\
\today

\vspace{0.1in}

\normalsize
\section{Response to Reviewer 1}

Thank you very much for the thoughtful and thorough review. We
responded to all comments in the annotated PDF, but this is our first
time using that tool so if there are any issues please let us know. As
an aside, thanks for introducing us to the annotated PDF feature. We
were not aware of it, and it was pleasant to use.

\section{Response to Reviewer 2}

As with reviewer 1, thank you very much for the time spent on a
thoughtful review. Here are responses to your comments:

\begin{enumerate}

\item This paper actually discusses transpiration not
  evapotranspiration - while the role of soil evaporation is sometimes
  acknowledged (and then dismissed) - it would be much cleaner if
  references to evapotranspiration (ET) were replaced with
  transpiration (T). The role of soil evaporation and interception in
  a changing climate is a whole other (and difficult!) issue.

  \textit{Response}: Yes, we agree that the underlying theory was
  developed for transpiration, and that it would probably appear
  cleaner to just present the manuscript in terms of transpiration
  instead of evapotranspiration. However, we prefer to use ET, along
  with the language discussing the theory's likely limitation when
  evaporation is high relative to transpiration, for a few of
  reasons. The parameter ranges we use in Table 2 for uWUE and g1 and
  are derived from ecosystem ET measurements in Zhou et al. 2015 and
  Medlyn et al. 2017, rather than T measurements. Given the
  semi-empirical nature of the theory, and that the parameters were
  developed empirically from ET observations rather than T
  observations (and it would require the reader to dig into cited
  literature to figure this out), we believe it is more transparent to
  call the quantity ET rather than T, while including explicit
  language about the possible weaknesses of the theory when
  evaporation is large relative to transpiration. Additionally, Zhou
  et al. 2014 and Zhou et al. 2015 use "ET" rather than "T", so by
  using "ET" we are more consistent with that notation. However,
  Medlyn et al. 2017 use "E" for this quantity (their Eq. 5), but call
  it "canopy transpiration," which we actually did not prefer because
  we felt using "transpiration" obfuscated the fact that their
  estimate of $g$ was actually derived from ET measurements. So, while
  we agree that it could appear cleaner to just call the quantity T
  and remove our language discussing the theory's limitations and
  caveats with respect to evaporation, we also believe this could hide
  the fact the we use semi-empirical parameters derived for ET, and
  distance our work from the previous work we directly build upon (in
  particular Zhou et al. 2014 and 2015). While not relevant at all
  (but still helpful in the end), keeping ET rather than adopting T
  has a practical advantage that our title would not need to be
  changed, which would help match the final peer reviewed version of
  the manuscript to already publicly available pre-prints of the
  manuscript.

\item Lines 80-90. Plants also use evaporation to cool their leaves - is
  this significant? And does it suggest there should be some residual
  stomatal opening?

  \textit{Response}: Yes, some plants use transpiration to regulate
  temperature on their leaves in some conditions, and this could be a
  cause of stomatal opening/closing. We added language at lines 78-80
  acknowledging that the simplified logic in the opening excludes
  details, including how plants can use transpiration for thermal
  regulation: ``...excludes many details ... e.g., ... thermal
  regulation with transpiration ... Lin et al. 2017''

\item Line 210-211. It would be worth expanding on the RH - es
  relationship - what data?

\textit{Response}: Agreed, we added a figure to the supplemental material on
    the relationship between RH and es, and a reference to it in the text.

\item Table 4 legend. Needs a bit of clarification on the choice of ranges
  of T and ga.

  \textit{Response}: Agreed; added clarifying language to the caption
  for how T and g$_a$ ranges were estimated (FLUXNET data): ``Values
  for $T$ and g$_a$ are calculated from FLUXNET-2015 data (see
  supplemental material for description), rounding the 15th, 50th, and
  85th percentile to the nearest 5$^o$C and 0.005 m/s, respectively.''

\item Line 322-335. I found this paragraph a bit ambiguous. The second
  sentence suggests most ptfs are similar to the median type but the
  following sentences suggest this is not true. I think this is
  important - the reader needs to know whether the max and min values
  of parameters are common or outliers.

\textit{Response}: Thanks; we reworded this paragraph to make it more clear and
    explicit: "...However, crops, shrubs, and grass are exceptions; they
    exhibit an uWUE different than the median value in Table 2. Crops,
    which we expect to prioritize carbon uptake over water conservation,
    have a higher uWUE value closer to our maximum value. This higher uWUE
    results in a higher likelihood for an increasing ET response to VPD,
    which matches intuition given that we expect crops to keep stomata
    open for access to carbon, at the cost of increased water loss during
    high VPD. Shrubs, and to a lesser extent grass, have an uWUE closer to
    the minimum uWUE. For these plant types, we would then expect a
    decrease of ET in response to VPD."

\item Supplementary material. As I say above I commend the inclusion of
  this 'negative' result.  However I would like to know how soil
  water was derived - is this measured or modelled and is it at the
  surface or through the entire rooting zone?

\textit{Response}: Yes, more clarity about the source of the data is
    helpful. We added language to the supplement explicitly stating that
    SWC is taken from the FLUXNET-2015 data; specifically the shallowest
    observed layer at each site: "For SWC measurements, we use the
    shallowest observed layer available at each site."
\end{enumerate}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-09-05 doc/paper/agu-james-submission-single-file.tex
done with submission

\begin{table}
  \caption{Variable quantities in the ET response to VPD. Each value
    is varied to determine the effect of a range of expected plant and
    environmental conditions on ET response to VPD. A citation is
    provided for values of g$_1$ and uWUE, which are directly derived
    from previous literature. Conceptually, min. values are extracted
    from literature to correspond to approximately the 15th percentile
    of observed conditions during the growing season, med. values
    correspond to approximately the 50th percentile, and max. values
    correspond to approximately the 85th percentile. Values for $T$
    and g$_a$ are calculated from FLUXNET-2015 data (see supplemental
    material for description), rounding the 15th, 50th, and 85th
    percentile to the nearest 5$^o$C and 0.005 m/s, respectively.}
  \label{param_varying}
  \centering
  \footnotesize
  \begin{tabular}{l c c c c c}
    \hline
    Symbol & units [units in citation] & min  & med & max
    & citation  \\
    \hline
    \input{param_varying.tex}
    \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Quantities that are fixed in the ET response to VPD
    (relative to those in Table \ref{param_varying}).}
  \label{param_fixed}
  \centering
  \begin{tabular}{l c c}
    \hline
    Symbol & units & value \\
    \hline
    \input{param_fixed.tex}
    \hline
  \end{tabular}
\end{table}

@@

\input{d2_solutions.tex}

@@

\bibliography{references}

>>>>

\begin{table}
  \caption{Variable quantities in the ET response to VPD. Each value
    is varied to determine the effect of a range of expected plant and
    environmental conditions on ET response to VPD. A citation is
    provided for values of g$_1$ and uWUE, which are directly derived
    from previous literature. Conceptually, min. values are extracted
    from literature to correspond to approximately the 15th percentile
    of observed conditions during the growing season, med. values
    correspond to approximately the 50th percentile, and max. values
    correspond to approximately the 85th percentile. Values for $T$
    and g$_a$ are calculated from FLUXNET-2015 data (see supplemental
    material for description), rounding the 15th, 50th, and 85th
    percentile to the nearest 5$^o$C and 0.005 m/s, respectively.}
  \label{param_varying}
  \centering
  \footnotesize
  \begin{tabular}{l c c c c c}
    \hline
    Symbol & units [units in citation] & min  & med & max
    & citation  \\
    \hline
g$_1$ & Pa$^{1/2}$ [kPa$^{1/2}$] & 63.25 [2.00] & 126.49 [4.00] & 189.74 [6.00] & Fig. 2, 7; \citeA{Medlyn_2017} \\
uWUE & $\mu$-mol C Pa$^{0.5}$ J$^{-1}$ ET [g C hPa$^{1/2}$ kg$^{-1}$ H$_2$O] & 2.33 [6.99] & 3.17 [9.52] & 4.01 [12.05] & Table 4; \citeA{Zhou_2015} \\
T & $^o$C & 10.00 & 20.00 & 30.00 & - \\
g$_a$ & m/s & 0.015 & 0.035 & 0.055 & - \\
    \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Quantities that are fixed in the ET response to VPD
    (relative to those in Table \ref{param_varying}).}
  \label{param_fixed}
  \centering
  \begin{tabular}{l c c}
    \hline
    Symbol & units & value \\
    \hline
P & Pa & 100000.00 \\
$\gamma$ & Pa K$^{-1}$ & 64.50 \\
R$_{air}$ & J  K$^{-1}$ kg$^{-1}$ & 288.00 \\
c$_a$ & $\mu$ mol CO$_2$ mol$^{-1}$ air & 400.00 \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{equation}
\frac{\partial^2 \; ET}{\partial \; VPD^2} = 0 \quad \forall \quad\frac{VPD^m}{g*} = \frac{m \left(m - 2 n - \sqrt{m^{2} - 4 m n + 2 m - 4 n^{2} + 4 n + 1} + 1\right)}{2 n \left(n - 1\right)} - 1.
\label{curves}
\end{equation}

@@

% \bibliography{references}

\begin{thebibliography}{}

\bibitem [\protect \citeauthoryear {%
Ball%
, Woodrow%
\BCBL {}\ \BBA {} Berry%
}{%
Ball%
\ \protect \BOthers {.}}{%
{\protect \APACyear {1987}}%
}]{%
Ball_1987}
\APACinsertmetastar {%
Ball_1987}%
\begin{APACrefauthors}%
Ball, J\BPBI T.%
, Woodrow, I\BPBI E.%
\BCBL {}\ \BBA {} Berry, J\BPBI A.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1987}{}{}.
\newblock
{\BBOQ}\APACrefatitle {A Model Predicting Stomatal Conductance and its
  Contribution to the Control of Photosynthesis under Different Environmental
  Conditions} {A model predicting stomatal conductance and its contribution to
  the control of photosynthesis under different environmental
  conditions}.{\BBCQ}
\newblock
\BIn{} \APACrefbtitle {Progress in Photosynthesis Research} {Progress in
  photosynthesis research}\ (\BPGS\ 221--224).
\newblock
\APACaddressPublisher{}{Springer Netherlands}.
\newblock
\begin{APACrefDOI} \doi{10.1007/978-94-017-0519-6\_48} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Berg%
\ \protect \BOthers {.}}{%
Berg%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2016}}%
}]{%
Berg_2016}
\APACinsertmetastar {%
Berg_2016}%
\begin{APACrefauthors}%
Berg, A.%
, Findell, K.%
, Lintner, B.%
, Giannini, A.%
, Seneviratne, S\BPBI I.%
, van~den Hurk, B.%
\BDBL {}Milly, P\BPBI C\BPBI D.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2016}{may}{}.
\newblock
{\BBOQ}\APACrefatitle {Land{\textendash}atmosphere feedbacks amplify aridity
  increase over land under global warming} {Land{\textendash}atmosphere
  feedbacks amplify aridity increase over land under global warming}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Nature Climate Change}{6}{9}{869--874}.
\newblock
\begin{APACrefDOI} \doi{10.1038/nclimate3029} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Berg%
, Sheffield%
\BCBL {}\ \BBA {} Milly%
}{%
Berg%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2017}}%
}]{%
Berg_2017}
\APACinsertmetastar {%
Berg_2017}%
\begin{APACrefauthors}%
Berg, A.%
, Sheffield, J.%
\BCBL {}\ \BBA {} Milly, P\BPBI C\BPBI D.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2017}{jan}{}.
\newblock
{\BBOQ}\APACrefatitle {Divergent surface and total soil moisture projections
  under global warming} {Divergent surface and total soil moisture projections
  under global warming}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Geophysical Research Letters}{44}{1}{236--244}.
\newblock
\begin{APACrefDOI} \doi{10.1002/2016gl071921} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Bouchet%
}{%
Bouchet%
}{%
{\protect \APACyear {1963}}%
}]{%
Bouchet_1963}
\APACinsertmetastar {%
Bouchet_1963}%
\begin{APACrefauthors}%
Bouchet, R\BPBI J.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1963}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Evapotranspiration r{\'e}elle et potentielle,
  signification climatique} {Evapotranspiration r{\'e}elle et potentielle,
  signification climatique}.{\BBCQ}
\newblock
\APACjournalVolNumPages{IAHS Publ}{62}{}{134--142}.
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Brooker%
}{%
Brooker%
}{%
{\protect \APACyear {2006}}%
}]{%
Brooker_2006}
\APACinsertmetastar {%
Brooker_2006}%
\begin{APACrefauthors}%
Brooker, R\BPBI W.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2006}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Plant–plant interactions and environmental change}
  {Plant–plant interactions and environmental change}.{\BBCQ}
\newblock
\APACjournalVolNumPages{New Phytologist}{171}{2}{271-284}.
\newblock
\begin{APACrefURL}
  \url{https://nph.onlinelibrary.wiley.com/doi/abs/10.1111/j.1469-8137.2006.01752.x}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1111/j.1469-8137.2006.01752.x} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Brutsaert%
}{%
Brutsaert%
}{%
{\protect \APACyear {1999}}%
}]{%
Brutsaert_1999}
\APACinsertmetastar {%
Brutsaert_1999}%
\begin{APACrefauthors}%
Brutsaert, W.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1999}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Aspects of bulk atmospheric boundary layer similarity
  under free-convective conditions} {Aspects of bulk atmospheric boundary layer
  similarity under free-convective conditions}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Reviews of {G}eophysics}{37}{4}{439--451}.
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Byrne%
\ \BBA {} O'Gorman%
}{%
Byrne%
\ \BBA {} O'Gorman%
}{%
{\protect \APACyear {2013}}%
}]{%
Byrne_2013}
\APACinsertmetastar {%
Byrne_2013}%
\begin{APACrefauthors}%
Byrne, M\BPBI P.%
\BCBT {}\ \BBA {} O'Gorman, P\BPBI A.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2013}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Land-Ocean Warming Contrast over a Wide Range of
  Climates: Convective Quasi-Equilibrium Theory and Idealized Simulations}
  {Land-ocean warming contrast over a wide range of climates: Convective
  quasi-equilibrium theory and idealized simulations}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Journal of Climate}{26}{12}{4000-4016}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1175/JCLI-D-12-00262.1}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1175/JCLI-D-12-00262.1} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Cowan%
\ \BBA {} Farquhar%
}{%
Cowan%
\ \BBA {} Farquhar%
}{%
{\protect \APACyear {1977}}%
}]{%
Cowan_1977}
\APACinsertmetastar {%
Cowan_1977}%
\begin{APACrefauthors}%
Cowan, I.%
\BCBT {}\ \BBA {} Farquhar, G.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1977}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Stomatal function in relation to leaf metabolism and
  environment.} {Stomatal function in relation to leaf metabolism and
  environment.}{\BBCQ}
\newblock
\BIn{} \APACrefbtitle {Symposia of the Society for Experimental Biology}
  {Symposia of the society for experimental biology}\ (\BVOL~31, \BPG~471).
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Cushman%
}{%
Cushman%
}{%
{\protect \APACyear {2001}}%
}]{%
Cushman_2001}
\APACinsertmetastar {%
Cushman_2001}%
\begin{APACrefauthors}%
Cushman, J\BPBI C.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2001}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Crassulacean Acid Metabolism. A Plastic Photosynthetic
  Adaptation to Arid Environments} {Crassulacean acid metabolism. a plastic
  photosynthetic adaptation to arid environments}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Plant Physiology}{127}{4}{1439--1448}.
\newblock
\begin{APACrefURL} \url{http://www.plantphysiol.org/content/127/4/1439}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1104/pp.010818} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Damour%
, Simonneau%
, Cochard%
\BCBL {}\ \BBA {} Urban%
}{%
Damour%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2010}}%
}]{%
Damour2010}
\APACinsertmetastar {%
Damour2010}%
\begin{APACrefauthors}%
Damour, G.%
, Simonneau, T.%
, Cochard, H.%
\BCBL {}\ \BBA {} Urban, L.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2010}{}{}.
\newblock
{\BBOQ}\APACrefatitle {An overview of models of stomatal conductance at the
  leaf level} {An overview of models of stomatal conductance at the leaf
  level}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Plant, Cell \& Environment}{33}{9}{1419-1438}.
\newblock
\begin{APACrefURL}
  \url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1365-3040.2010.02181.x}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1111/j.1365-3040.2010.02181.x} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
De~Kauwe%
, Medlyn%
, Knauer%
\BCBL {}\ \BBA {} Williams%
}{%
De~Kauwe%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2017}}%
}]{%
De_2017}
\APACinsertmetastar {%
De_2017}%
\begin{APACrefauthors}%
De~Kauwe, M\BPBI G.%
, Medlyn, B\BPBI E.%
, Knauer, J.%
\BCBL {}\ \BBA {} Williams, C\BPBI A.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2017}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Ideas and perspectives: how coupled is the vegetation to
  the boundary layer?} {Ideas and perspectives: how coupled is the vegetation
  to the boundary layer?}{\BBCQ}
\newblock
\APACjournalVolNumPages{Biogeosciences}{14}{19}{4435}.
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
De~Schepper%
, De~Swaef%
, Bauweraerts%
\BCBL {}\ \BBA {} Steppe%
}{%
De~Schepper%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2013}}%
}]{%
De_2013}
\APACinsertmetastar {%
De_2013}%
\begin{APACrefauthors}%
De~Schepper, V.%
, De~Swaef, T.%
, Bauweraerts, I.%
\BCBL {}\ \BBA {} Steppe, K.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2013}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Phloem transport: a review of mechanisms and controls}
  {Phloem transport: a review of mechanisms and controls}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Journal of Experimental Botany}{64}{16}{4839--4850}.
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
G.~Farquhar%
}{%
G.~Farquhar%
}{%
{\protect \APACyear {1978}}%
}]{%
Farquhar_1978}
\APACinsertmetastar {%
Farquhar_1978}%
\begin{APACrefauthors}%
Farquhar, G.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1978}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Feedforward responses of stomata to humidity}
  {Feedforward responses of stomata to humidity}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Functional Plant Biology}{5}{6}{787--800}.
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
G\BPBI D.~Farquhar%
, von Caemmerer%
\BCBL {}\ \BBA {} Berry%
}{%
G\BPBI D.~Farquhar%
\ \protect \BOthers {.}}{%
{\protect \APACyear {1980}}%
}]{%
Farquhar_1980}
\APACinsertmetastar {%
Farquhar_1980}%
\begin{APACrefauthors}%
Farquhar, G\BPBI D.%
, von Caemmerer, S.%
\BCBL {}\ \BBA {} Berry, J\BPBI A.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1980}{Jun}{01}.
\newblock
{\BBOQ}\APACrefatitle {A biochemical model of photosynthetic {CO}2 assimilation
  in leaves of {C}3 species} {A biochemical model of photosynthetic {CO}2
  assimilation in leaves of {C}3 species}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Planta}{149}{1}{78--90}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1007/BF00386231} \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1007/BF00386231} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Franks%
, Berry%
, Lombardozzi%
\BCBL {}\ \BBA {} Bonan%
}{%
Franks%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2017}}%
}]{%
Franks_2017}
\APACinsertmetastar {%
Franks_2017}%
\begin{APACrefauthors}%
Franks, P\BPBI J.%
, Berry, J\BPBI A.%
, Lombardozzi, D\BPBI L.%
\BCBL {}\ \BBA {} Bonan, G\BPBI B.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2017}{apr}{}.
\newblock
{\BBOQ}\APACrefatitle {Stomatal Function across Temporal and Spatial Scales:
  Deep-Time Trends, Land-Atmosphere Coupling and Global Models} {Stomatal
  function across temporal and spatial scales: Deep-time trends,
  land-atmosphere coupling and global models}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Plant Physiology}{174}{2}{583--602}.
\newblock
\begin{APACrefDOI} \doi{10.1104/pp.17.00287} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Gentine%
, Chhang%
, Rigden%
\BCBL {}\ \BBA {} Salvucci%
}{%
Gentine%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2016}}%
}]{%
Gentine_2016}
\APACinsertmetastar {%
Gentine_2016}%
\begin{APACrefauthors}%
Gentine, P.%
, Chhang, A.%
, Rigden, A.%
\BCBL {}\ \BBA {} Salvucci, G.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2016}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Evaporation estimates using weather station data and
  boundary layer theory} {Evaporation estimates using weather station data and
  boundary layer theory}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Geophysical Research Letters}{43}{22}{11,661--11,670}.
\newblock
\begin{APACrefURL} \url{http://dx.doi.org/10.1002/2016GL070819}
  \end{APACrefURL}
\newblock
\APACrefnote{2016GL070819}
\newblock
\begin{APACrefDOI} \doi{10.1002/2016GL070819} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
P.~Jarvis%
}{%
P.~Jarvis%
}{%
{\protect \APACyear {1984}}%
}]{%
Jarvis_1984}
\APACinsertmetastar {%
Jarvis_1984}%
\begin{APACrefauthors}%
Jarvis, P.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1984}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Coupling of transpiration to the atmosphere in
  horticultural crops: the omega factor} {Coupling of transpiration to the
  atmosphere in horticultural crops: the omega factor}.{\BBCQ}
\newblock
\BIn{} \APACrefbtitle {I International Symposium on Water Relations in Fruit
  Crops 171} {I international symposium on water relations in fruit crops 171}\
  (\BPGS\ 187--206).
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
P\BPBI G.~Jarvis%
\ \BBA {} McNaughton%
}{%
P\BPBI G.~Jarvis%
\ \BBA {} McNaughton%
}{%
{\protect \APACyear {1986}}%
}]{%
Jarvis_1986}
\APACinsertmetastar {%
Jarvis_1986}%
\begin{APACrefauthors}%
Jarvis, P\BPBI G.%
\BCBT {}\ \BBA {} McNaughton, K.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1986}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Stomatal control of transpiration: scaling up from leaf
  to region} {Stomatal control of transpiration: scaling up from leaf to
  region}.{\BBCQ}
\newblock
\BIn{} \APACrefbtitle {Advances in Ecological Research} {Advances in ecological
  research}\ (\BVOL~15, \BPGS\ 1--49).
\newblock
\APACaddressPublisher{}{Elsevier}.
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
G.~Katul%
, Manzoni%
, Palmroth%
\BCBL {}\ \BBA {} Oren%
}{%
G.~Katul%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2010}}%
}]{%
Katul_2010}
\APACinsertmetastar {%
Katul_2010}%
\begin{APACrefauthors}%
Katul, G.%
, Manzoni, S.%
, Palmroth, S.%
\BCBL {}\ \BBA {} Oren, R.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2010}{}{}.
\newblock
{\BBOQ}\APACrefatitle {A stomatal optimization theory to describe the effects
  of atmospheric {CO}2 on leaf photosynthesis and transpiration} {A stomatal
  optimization theory to describe the effects of atmospheric {CO}2 on leaf
  photosynthesis and transpiration}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Annals of Botany}{105}{3}{431-442}.
\newblock
\begin{APACrefURL} \url{+ http://dx.doi.org/10.1093/aob/mcp292}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1093/aob/mcp292} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
G\BPBI G.~Katul%
, Palmroth%
\BCBL {}\ \BBA {} Oren%
}{%
G\BPBI G.~Katul%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2009}}%
}]{%
Katul_2009}
\APACinsertmetastar {%
Katul_2009}%
\begin{APACrefauthors}%
Katul, G\BPBI G.%
, Palmroth, S.%
\BCBL {}\ \BBA {} Oren, R.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2009}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Leaf stomatal responses to vapour pressure deficit under
  current and CO2-enriched atmosphere explained by the economics of gas
  exchange} {Leaf stomatal responses to vapour pressure deficit under current
  and co2-enriched atmosphere explained by the economics of gas
  exchange}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Plant, Cell \& Environment}{32}{8}{968-979}.
\newblock
\begin{APACrefURL}
  \url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1365-3040.2009.01977.x}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1111/j.1365-3040.2009.01977.x} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Lawrence%
\ \protect \BOthers {.}}{%
Lawrence%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2019}}%
}]{%
Lawrence_2019}
\APACinsertmetastar {%
Lawrence_2019}%
\begin{APACrefauthors}%
Lawrence, D.%
, Fisher, R.%
, Koven, C.%
, Oleson, K.%
, Swenson, S.%
, Bonan, G.%
\BDBL {}Zeng, X.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2019}{}{}.
\newblock
{\BBOQ}\APACrefatitle {The Community Land Model version 5: Description of new
  features, benchmarking, and impact of forcing uncertainty} {The community
  land model version 5: Description of new features, benchmarking, and impact
  of forcing uncertainty}.{\BBCQ}
\newblock
\APACjournalVolNumPages{submitted to Journal of Advances in Modeling Earth
  Systems}{}{}{}.
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Lemordant%
, Gentine%
, Swann%
, Cook%
\BCBL {}\ \BBA {} Scheff%
}{%
Lemordant%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2018}}%
}]{%
Lemordant_2018}
\APACinsertmetastar {%
Lemordant_2018}%
\begin{APACrefauthors}%
Lemordant, L.%
, Gentine, P.%
, Swann, A\BPBI S.%
, Cook, B\BPBI I.%
\BCBL {}\ \BBA {} Scheff, J.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2018}{apr}{}.
\newblock
{\BBOQ}\APACrefatitle {Critical impact of vegetation physiology on the
  continental hydrologic cycle in response to increasing {CO}2} {Critical
  impact of vegetation physiology on the continental hydrologic cycle in
  response to increasing {CO}2}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Proceedings of the National Academy of
  Sciences}{}{}{201720712}.
\newblock
\begin{APACrefURL} \url{https://doi.org/10.1073\%2Fpnas.1720712115}
  \end{APACrefURL}
\newblock
\begin{APACrefDOI} \doi{10.1073/pnas.1720712115} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
Leuning%
}{%
Leuning%
}{%
{\protect \APACyear {1990}}%
}]{%
Leuning_1990}
\APACinsertmetastar {%
Leuning_1990}%
\begin{APACrefauthors}%
Leuning, R.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{1990}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Modelling Stomatal Behaviour and and Photosynthesis {of
  Eucalyptus} grandis} {Modelling stomatal behaviour and and photosynthesis {of
  Eucalyptus} grandis}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Australian Journal of Plant Physiology}{17}{2}{159}.
\newblock
\begin{APACrefDOI} \doi{10.1071/pp9900159} \end{APACrefDOI}
\PrintBackRefs{\CurrentBib}

\bibitem [\protect \citeauthoryear {%
C.~Lin%
\ \protect \BOthers {.}}{%
C.~Lin%
\ \protect \BOthers {.}}{%
{\protect \APACyear {2018}}%
}]{%
Lin_2018}
\APACinsertmetastar {%
Lin_2018}%
\begin{APACrefauthors}%
Lin, C.%
, Gentine, P.%
, Huang, Y.%
, Guan, K.%
, Kimm, H.%
\BCBL {}\ \BBA {} Zhou, S.%
\end{APACrefauthors}%
\unskip\
\newblock
\APACrefYearMonthDay{2018}{}{}.
\newblock
{\BBOQ}\APACrefatitle {Diel ecosystem conductance response to vapor pressure
  deficit is suboptimal and independent of soil moisture} {Diel ecosystem
  conductance response to vapor pressure deficit is suboptimal and independent
  of soil moisture}.{\BBCQ}
\newblock
\APACjournalVolNumPages{Agricultural and Forest Meteorology}{250}{}{24--34}.
\PrintBackRefs{\CurrentBib}
